Main text : Effect of copula on extinction risk

### 2019-03-12 MainText.Rmd
adding C-SC-G-SG linear age structured plots
started writing methods

@@

 <!--FIG : age structure model results : linear, nonlinear-->
\begin{figure*}[!h]
\textbf{ \hspace{5.4 cm} (A) \hspace{4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured $(A)$ linear ($\Omega = \infty$) and $(B)$ nonlinear ($\Omega = 100$) models, fecundity of adults and survival of eggs have either extreme left or extreme right tail dependence, numsims=10000. \label{fig_extrisk_agestr}}
\end{center}
\end{figure*}

>>>>

<!--stochastic matrix model : age structured-->
To investigate how copula structure in noisy environment affect the extinction risk of
populations in a single patch age-structured model,
we considered a simple stochastic age-structured model (Eq. \ref{eq_age_str}) 
with two age classes: 
one is egg ($E$) and the other is adult ($A$). We assumed
the population was semelperous, i.e., adult ($A$) went through the
reproductive episode only once before death. Eggs and adults in the 
next generation depend upon the fecundity of adult ($f_a \geq 0$) 
and survival of eggs ($0 \leq s_e \leq 1$) from present generation, respectively.
The environmental stochasticity in the model was embedded in 
the fluctuating vital rates ($f_a$ and $s_e$). We considered the fecundity ($f_a$)
and survival ($s_e$) rates were random draw from a gamma ($\Gamma(k,\theta)$) and
a beta ($\mathcal{B}(\alpha,\beta)$) distribution, respectively,
which were generated from a specific tail-dependent copula
(for details see Appendix \ref{SM-age_str_vitalrates}).
Eq. \ref{eq_vitalrates} represent the stochasticity in the vital rates.
Demographic stochasticity was also taken into consideration when we included the 
density dependence effect in one of the vital rate, namely, fecundity ($f_a$).
If $\Omega = \infty$ in Eq. \ref{eq_vitalrates}, the projection matrix was independent
of populations from any age-class and the model was then called to be "linear", whereas
its "nonlinear" version had finite $\Omega$.

\begin{equation}
\left({\begin{array}{cc} E \\ A \end{array}}\right)_{t+1} = 
\left(\begin{array}{cc} 0 & f_a\\ s_e & 0 \end{array}\right)
\left(\begin{array}{c} E \\ A \end{array}\right)_{t} \label{eq_age_str}
\end{equation}

\begin{equation}
f_a = \Gamma (k, \theta)\exp(-A/\Omega), \hspace{0.2 cm} s_e = \mathcal{B}(\alpha,\beta) \label{eq_vitalrates}
\end{equation}

<!--calculation of ext risk with age-structured model-->

<!--density-dependence metapopulation model-->

<!--calculation of ext risk with density-dependence metapopulation model-->

@@

 <!--FIG : age structure model results : linear, nonlinear-->

\begin{figure*}[!h]
\textbf{ \hspace{5.4 cm} (A) \hspace{4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured $(A)$ linear ($\Omega = \infty$) and $(B)$ nonlinear ($\Omega = 100$) models, fecundity of adults and survival of eggs have either extreme left or extreme right tail dependence, numsims=10000. \label{fig_extrisk_agestr}}
\end{center}
\end{figure*}
